Precise spiking motifs in neurobiological and neuromorphic data

### 2022-11-15 manuscript.tex
Update on Overleaf.

There are more applications to image processing using spiking neural networks based on the design of micro-circuits with specific lateral interactions embedded with spatially anisotropic connections. Using this core computational unit defined, and extending to computations on a topographic representation similar to that observed in the primary visual cortex of mammals, the anisotropic rules implemented a form of delayed activation. This result was based on a predictive model defined in the Bayesian framework (the so-called free-energy principle) which was able to account for temporal delays in the  system, both at the sensory and motor levels~\citep{perrinet_active_2014}, and in particular that ``the application of delay operators just means changing synaptic connection strengths to take different mixtures of generalized sensations and their prediction errors.'' Such a model was implemented at the network level and applied to various motion detection tasks. Two neurons which were selective to specific motions were connected if the delay was coherent with the change in the position of their respective receptive fields~\citep{hogendoorn_predictive_2019}.  This was also implemented in a neural mass model, showing that such anisotropic connectivity may explain the emergence of tracking~\citep{khoei_motion-based_2013}, and further explored in a spiking neural network which reproduced the observation that neural activity was maintained during the trajectory of a smoothly moving dot even if it was momentarily blanked~\citep{kaplan_anisotropic_2013}. This led in particular to the proposal that such delay-based computations could explain diverse perceptual mechanisms, such as the so-called flash-lag illusion~\citep{khoei_flash-lag_2017}. However, these latter models used parametric rules for defining the weights. Extending such mechanisms with the ability of learning delays in a SNN will provide a breakthrough in the efficiency of these networks, and we will explore results from neuromorphic engineering to get better insights on that aspect.

>>>>

There are more applications to image processing using spiking neural networks. For instance, a set of models are based on the design of micro-circuits with specific lateral interactions embedded with spatially anisotropic connections. Using this core computational unit, and extending it to computations on a topographic representation similar to that observed in the primary visual cortex of mammals, the anisotropic rules implemented a form of delayed activation. This result was based on a predictive model defined in the Bayesian framework (the so-called free-energy principle) which was able to account for temporal delays in the  system, both at the sensory and motor levels~\citep{perrinet_active_2014}, and in particular that ``the application of delay operators just means changing synaptic connection strengths to take different mixtures of generalized sensations and their prediction errors.'' Such a model was implemented at the network level and applied to various motion detection tasks. In essence, two neurons which were selective to specific motions were connected if the delay was coherent with the change in the position of their respective receptive fields~\citep{hogendoorn_predictive_2019}.  This was also implemented in a neural mass model, showing that such anisotropic connectivity may explain the emergence of tracking~\citep{khoei_motion-based_2013}, and further explored in a spiking neural network which reproduced the observation that neural activity was maintained during the trajectory of a smoothly moving dot even if it was momentarily blanked~\citep{kaplan_anisotropic_2013}. This led in particular to the proposal that such delay-based computations could explain diverse perceptual mechanisms, such as the so-called flash-lag illusion~\citep{khoei_flash-lag_2017}. However, these latter models used parametric rules for defining the weights. Extending such mechanisms with the ability of learning delays in a SNN will provide a breakthrough in the efficiency of these networks, and we will explore some exemplar results from neuromorphic engineering to get better insights on that aspect.
